Wrangle

### 2023-09-26 wrangle.qmd
Continuous time analysis (#7)
add continuous time analyses

---------

Co-authored-by: Kristoffer Magnusson <1629860+rpsychologist@users.noreply.github.com>
Add some text

@@

library(tidyverse)
source("functions.R")
```

@@

@@

```{r}
dir.create("data", FALSE)
saveRDS(dat, "data/data.rds")
saveRDS(dat_raw, "data/data-raw.rds")
saveRDS(s, "data/s.rds")
saveRDS(sraw, "data/sraw.rds")
```

>>>>

Load some packages:

@@

library(patchwork)
library(tidyverse)
source("R/functions.R")
```

## Raw data

Download data from OSF:

@@

Load data and rename and rescale variables:

@@

## Save data

```{r}
dir.create("data", FALSE)
saveRDS(dat, "data/data.rds")
```
